The 2018 heatwave and its implications on ozone induced damage on vegetation in a subartic climate

### 2020-03-24 VegOzone.tex
Included plots.

\Author[1]{Stefanie}{Falk}
\Author[2]{Ane Victoria}{Vollsnes}
\author[3]{Lisa}{Emberson}
\Author[1]{Frode}{Stordal}

@@

\section{Data}
TEXT
\begin{figure}[t]
\includegraphics[width=8.3cm]{station_map_fennoscandia}
\caption{Cap of the North. Reasearch stations with given ozone time series in northern Fennoscandia.}
\end{figure}

@@

\subsection{Observational data}
Table: EBAS - Station list
\begin{figure*}[t]
  \includegraphics[width=12cm]{ozone_timeseries_fenoscandic_obs.png}

  \caption{Timeseries of ozone observations in northern Fennoscadia. Data taken from EBAS and ozone monitoring at Svanhovd in the summer seasons 2018/19. The hatched area indicates time periods with unsufficient quality control - cite: NILU ozone report 200x.}
\end{figure*}

\subsection{Model and reanalysis data}
TEXT
\begin{figure}[t]
  \includegraphics[width=8.3cm]{ozone_climatologies}

  \caption{Comparison of observational data with various ozone reanlysis products.}
\end{figure}

@@

@@

\section{DO3SE modeling}
Model results for natural and semi-natural vegetation (birch, pine, clover)
\begin{itemize}
\item climatological ozone impact
\item 2018
\item 2019
\end{itemize}

@@

\appendixfigures  %% needs to be added in front of appendix figures

>>>>

\Author[1]{Stefanie}{Falk}
\Author[2]{Ane Victoria}{Vollsnes}
\Author[3]{Lisa}{Emberson}
\Author[1]{Frode}{Stordal}

@@

\section{Data}
TEXT
\begin{figure}[t]
  \includegraphics[width=8.3cm]{station_map_fennoscandia}
  \label{fig:station_map_fennoscandia}
\caption{Cap of the North. Reasearch stations with given ozone time series in northern Fennoscandia.}
\end{figure}

@@

\subsection{Observational data}
Table: EBAS - Station list
\begin{figure*}[t]
  \includegraphics[width=12cm]{ozone_timeseries_fenoscandic_obs.png}
  \label{fig:ozone_timesseries_fenoscandic_obs}
  \caption{Timeseries of ozone observations in northern Fennoscadia. Data taken from EBAS and ozone monitoring at Svanhovd in the summer seasons 2018/19. The hatched area indicates time periods with unsufficient quality control - cite: NILU ozone report 200x.}
\end{figure*}

\subsection{Model and reanalysis data}
Ozone: MACC-rea, CAMS-rea, Copernicus European regional model rea
Precipitation/Temperature: CRU biascorrected rea
Ozone uptake / POD: DO3SE

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{ozone_climatology_fenoscandic_obs}
  \label{fig:ozone_climatology_fenoscandic_obs}
  \caption{Comparison of observational data with various ozone reanlysis products.}
\end{figure}

\begin{figure}[t]
  \includegraphics[width=8.3cm]{ozone_climatologies}
  \label{fig:ozone_climatologies}
  \caption{Comparison of observational data with various ozone reanlysis products.}
\end{figure}

\begin{figure}[t]
  \includegraphics[width=8.3cm]{ozone_climatology_fenoscandic_obs_spline}
  \label{fig:ozone_climatology_fenoscandic_obs_spline}
\caption{Cap of the North. Reasearch stations with given ozone time series in northern Fennoscandia.}
\end{figure}

\begin{figure}[t]
  \includegraphics[width=8.3cm]{ozone_climatology_fenoscandic_obs_residuals}
  \label{fig:ozone_climatology_fenoscandic_obs_residuals}
\caption{Cap of the North. Reasearch stations with given ozone time series in northern Fennoscandia.}
\end{figure}

\begin{figure}[t]
  \includegraphics[width=8.3cm]{ozone_climatology_fenoscandic_obs_residuals-Svanvik}
  \label{fig:ozone_climatology_fenoscandic_obs_residuals-Svanvik}
\caption{Cap of the North. Reasearch stations with given ozone time series in northern Fennoscandia.}
\end{figure}

\begin{figure}[t]
  \includegraphics[width=8.3cm]{ozone_climatology_fenoscandic_obs_test}
  \label{fig:ozone_climatology_fenoscandic_obs_test}
\caption{Cap of the North. Reasearch stations with given ozone time series in northern Fennoscandia.}
\end{figure}

\begin{figure}[t]
  \includegraphics[width=8.3cm]{ozone_climatology_fenoscandic_obs_test-Svanvik}
  \label{fig:ozone_climatology_fenoscandic_obs_test-Svanvik}
\caption{Cap of the North. Reasearch stations with given ozone time series in northern Fennoscandia.}
\end{figure}

\begin{figure}[t]
  \includegraphics[width=8.3cm]{plot_temperature_anomalies_svanvik}
  \label{fig:plot_temperature_anomalies_svanvik}
\caption{Cap of the North. Reasearch stations with given ozone time series in northern Fennoscandia.}
\end{figure}

\begin{figure}[t]
  \includegraphics[width=8.3cm]{plot_precipitation_anomalies_svanvik}
  \label{fig:plot_precipitation_anomalies_svanvik}
\caption{Cap of the North. Reasearch stations with given ozone time series in northern Fennoscandia.}
\end{figure}

@@

\section{DO3SE modeling}
\begin{figure}[t]
  \includegraphics[width=8.3cm]{ozone_obs_2018_07}
  \label{fig:ozone_obs_2018_07}
\caption{Cap of the North. Reasearch stations with given ozone time series in northern Fennoscandia.}
\end{figure}
Model results for natural and semi-natural vegetation (birch, pine, clover)
\begin{itemize}
\item climatological ozone impact
\item 2018
\item 2019
\end{itemize}

@@

\appendixfigures  %% needs to be added in front of appendix figures
\begin{figure}[t]
  \includegraphics[width=8.3cm]{greening_season_change_Svanvik}
  \label{fig:greening_season_change_Svanvik}
\caption{Cap of the North. Reasearch stations with given ozone time series in northern Fennoscandia.}
\end{figure}

\begin{figure}[t]
  \includegraphics[width=8.3cm]{test_fennoscandia}
  \label{fig:test_fennoscandia}
\caption{Cap of the North. Reasearch stations with given ozone time series in northern Fennoscandia.}
\end{figure}

\begin{figure}[t]
  \includegraphics[width=8.3cm]{density_distribution}
  \label{fig:density_distribution}
\caption{Cap of the North. Reasearch stations with given ozone time series in northern Fennoscandia.}
\end{figure}

\begin{figure}[t]
  \includegraphics[width=8.3cm]{ozone_obs_2018_07}
  \label{fig:ozone_obs_2018_rrea}
\caption{Cap of the North. Reasearch stations with given ozone time series in northern Fennoscandia.}
\end{figure}
